\sysfull

### 2018-04-17 paper/hwswsetup.tex
methodology typos

Experiments on the intermittently-powered platform used the
WISP\,5.1~\cite{wisp5,wisp} RF-powered energy-harvesting device.
%
The WISP contains the MSP430FR5969~\cite{wolverine} MCU with 64\,kB of
non-volatile (FRAM) memory and 2\,kB of volatile (SRAM) memory and was
configured to 1\,MHz clock speed.
%
We powered the WISP using an RF signal generator emitting  a 20-\,dBm sinusoidal wave at 915\,MHz.
The signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic
antenna~\cite{atlas2015}.
%
The antenna was oriented towards and in parallel with the WISP antenna, and
no objects obstructed the path.
%
We affixed the WISP with a paper harness at the edge of a table, so that the
WISP was parallel to the table surface at a height of 10\,cm.
%
For distance-controlled experiments we positioned the signal generator
antenna at a fixed distance from the WISP. The distances were $d=\{15, 30,
50\}$\,cm for the main experiments and 60\,cm for the task downscaling
experiments.
%
We chose relatively shorter distances than in a deployment scenario to reduce
charge time and run experiments faster, after having confirmed ourselves a
result also reported in prior work~\cite{alpaca} that the amount of energy
available in one charge cycle --- the sum of stored energy and incoming energy
during execution -- is the same at distances beyond 50~cm where incoming energy
becomes negligible.
%
To obtain execution time, the software toggled GPIO pins at sections of the code
under profile, and the Saleae~\cite{saleae} logic analyzer measured
the interval between edges in the signal.

>>>>

Experiments on the intermittently-powered platform used the
WISP\,5.1~\cite{wisp5,wisp} RF-powered energy-harvesting device.
%
The WISP contains the MSP430FR5969~\cite{wolverine} MCU with 64\,kB of
non-volatile (FRAM) memory and 2\,kB of volatile (SRAM) memory and was
configured to 1\,MHz clock speed.
%
We powered the WISP using an RF signal generator emitting  a 20-\,dBm sinusoidal wave at 915\,MHz.
The signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic
antenna~\cite{atlas2015}.
%
The antenna was oriented towards and in parallel with the WISP antenna, and
no objects obstructed the path.
%
We affixed the WISP with a paper harness at the edge of a table, so that the
WISP was parallel to the table surface at a height of 10\,cm.
%
For distance-controlled experiments we positioned the signal generator
antenna at a fixed distance from the WISP. The distances were $d=\{15, 30,
50\}$\,cm for the main experiments and 60\,cm for the task downscaling
experiments.
%
We chose relatively shorter distances than in a deployment scenario to reduce
charge time and run experiments faster, after having confirmed ourselves a
result also reported in prior work~\cite{alpaca} that the amount of energy
available in one charge cycle---the sum of stored energy and incoming energy
during execution---is the same at distances beyond 50\,cm where incoming energy
becomes negligible.
%
To obtain execution time, the software toggled GPIO pins at sections of the code
under profile, and the Saleae~\cite{saleae} logic analyzer measured
the interval between edges in the signal.
